Title

### 2018-08-29 thesis/paper/paper.tex
Improved none of

\subsection{None of (Q52558054)}
The none of constraint restricts the values that the property may refer to by listing a set of values as forbidden.

\begin{table}[H]
\caption{None of constraint (Q52558054)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & constrained statement \\
\hline
Qualifiers & \makecell{forbidden value (P2305) -- 1..* \\ values that may not appear in a constrained property} \\
\hline
Violation & \makecell{constrained statement with a forbidden value} \\
\hline
Dependency & constrained statement \\
\hline
\end{tabularx}
\end{table}

Modelling this constraint is very straightforward, since each forbidden value forms a property-value pair with the constrained statement that may not exists. Thus a violations is a statementEDB with the constrained statement and a forbidden value.

@@

\subsection{None of (Q52558054)}
The none of constraint simply forbids certain values for properties, thus effectively prohibiting certain triples, qualifiers and references. The violations, depending on nothing but specific database entries, are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}

>>>>

\subsection{None of (Q52558054)}
\subsubsection{Constraint}
The none of constraint restricts the values that the property may refer to by listing a set of values as forbidden.

\begin{table}[H]
\caption{None of constraint (Q52558054)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Required data & constrained statements, qualifiers and references \\
\hline
Qualifiers & \makecell{\emph{forbidden value} (P2305) -- 1..* \\ values that may not be object of a constraint statement, qualifier or reference} \\
\hline
Violation & \makecell{constrained statement, qualifier or reference with a forbidden value} \\
\hline
\end{tabularx}
\end{table}

\subsubsection{Rules}
The none of constraint simply forbids certain values for properties, thus effectively prohibiting certain triples, qualifiers and references. The rules, depending on nothing but specific database entries, are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{statementEDB}(S, I, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, \text{forbiddenValueConstant}) \leftarrow \\
&\text{referenceEDB}(S, H, \text{propertyConstant}, \text{forbiddenValueConstant})
\end{split}
\end{equation*}
Given a specified constraint, each of the three rules is created once for each \emph{forbidden value}.

@@
